Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/table-data.tex
table-data.tex fix times
remove automata with 0-1 acc. marks

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\389/404 solved aut.\\538 acc. marks}}
&
level 1 &
421 & 21.75 & 419.2 & 389 & 0
\\
&
level 2 &
421 & 21.75 & 14.13 & 389 & 0
\\
&
level 3 &
412 & 23.42 & 232.98 & 382 & 7
\\
&
multi &
412 & 23.42 & 686.96 & 383 & 6
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\371/376 solved aut.\\562 acc. marks}}
&
level 1 &
546 & 2.85 & 783.19 & 353 & 18
\\
&
level 2 &
548 & 2.49 & 80.53 & 351 & 20
\\
&
level 3 &
540 & 3.91 & 163.15 & 346 & 25
\\
&
multi &
537 & 4.45 & 2295.88 & 346 & 25
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\388/397 solved aut.\\766 acc. marks}}
&
level 1 &
553 & 27.81 & 898.88 & 370 & 18
\\
&
level 2 &
563 & 26.5 & 99.36 & 367 & 21
\\
&
level 3 &
569 & 25.72 & 355.55 & 357 & 31
\\
&
multi &
541 & 29.37 & 2538.7 & 361 & 27
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\378/386 solved aut.\\1084 acc. marks}}
&
level 1 &
616 & 43.17 & 828.84 & 362 & 16
\\
&
level 2 &
627 & 42.16 & 132.48 & 358 & 20
\\
&
level 3 &
627 & 42.16 & 194.59 & 352 & 26
\\
&
multi &
606 & 44.1 & 2339.83 & 352 & 26
\\

>>>>

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\79/89 solved aut.\\236 acc.~marks}}
&
level 1 &
236 & 0.0 & 269.4 & 79 & 0
\\
&
level 2 &
236 & 0.0 & 284.4 & 79 & 0
\\
&
level 3 &
227 & 3.8 & 517.4 & 72 & 7
\\
&
multi &
227 & 3.8 & 537.4 & 73 & 6
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\103/108 solved aut.\\419 acc.~marks}}
&
level 1 &
403 & 3.8 & 658.2 & 85 & 18
\\
&
level 2 &
405 & 3.3 & 738.9 & 83 & 20
\\
&
level 3 &
397 & 5.3 & 901.5 & 78 & 25
\\
&
multi &
394 & 6.0 & 2170.6 & 78 & 25
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\153/162 solved aut.\\618 acc.~marks}}
&
level 1 &
435 & 29.6 & 788.4 & 135 & 18
\\
&
level 2 &
445 & 28.0 & 887.7 & 132 & 21
\\
&
level 3 &
451 & 27.0 & 1243.3 & 122 & 31
\\
&
multi &
423 & 31.6 & 2427.8 & 126 & 27
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\266/274 solved aut.\\972 acc.~marks}}
&
level 1 &
606 & 37.7 & 774.2 & 250 & 16
\\
&
level 2 &
617 & 36.5 & 906.6 & 246 & 20
\\
&
level 3 &
617 & 36.5 & 1101.0 & 240 & 26
\\
&
multi &
596 & 38.7 & 2285.3 & 240 & 26
\\
